Jeff Goldsmith

### 2017-04-20 git.Rmd
embedded slides for content

>>>>

<script async class="speakerdeck-embed" data-id="b1f65532f0644b8fb5301f8fd6934b01" data-ratio="1.33333333333333" src="//speakerdeck.com/assets/embed.js"></script>
<div style="margin-bottom:5px"> <strong> <a href="https://speakerdeck.com/jeffgoldsmith/git-slides" title="Git stuff" target="_blank">Git stuff</a> </strong> from <strong><a href="https://speakerdeck.com/jeffgoldsmith" target="_blank">Jeff Goldsmith</a></strong>. </div>
